Drake Plan

### 2020-07-10 R/drake_plan_conus.Rmd
install/update drake & SHAPforxgboost

# Write the plan

```{r}
# See `drake_funcs.R` for functions used in this drake plan #

@@

# Libraries
# if needed, update drake
if(packageVersion("drake") < "7.4") install.packages("drake")
if(packageVersion("SHAPforxgboost") < "0.0.2") devtools::install_github("liuyanguu/SHAPforxgboost")

suppressPackageStartupMessages({
  library(sf)
  library(magrittr)
  library(drake)
  library(data.table)
  library(fst)
  library(future)
  library(here)
  library(nngeo)
  library(ggplot2)
  library(SHAPforxgboost)
})
# ** need to revise accordingly the path to your local clone of Just_universal **
source(here("../Just_universal/code/xgboost_cvtune.R"))
source(here("../Just_universal/code/xgboost_cv_RFE.R"))

>>>>

Handle checking for installed and out of date packages without attaching their namespace
```{r check_and_install_pkgs}
package_install <- function(pkg, version, github_source = NULL){
  if(!is.null(github_source)){
    remotes::install_github(github_source)
  } else {
    install.packages(pkg)
  }}
check_and_install <- function(pkg, version, github_source = NULL){
  tryCatch(
    if(packageVersion(pkg) < version) package_install(pkg, version, github_source), 
  error = function(e) {
    if(substr(e$message, 1, 26) == "there is no package called"){
      package_install(pkg, version, github_source)
    } else {
      message(e)
    }
  })}
```

# Write the plan
```{r}
# See `drake_funcs.R` for functions used in this drake plan #

@@

# Libraries
# if needed, update drake
if(!require(remotes)) install.packages("remotes")
check_and_install("drake", "7.4")
check_and_install("SHAPforxgboost", "0.0.2", "liuyanguu/SHAPforxgboost")

suppressPackageStartupMessages({
  library(sf)
  library(magrittr)
  library(drake)
  library(data.table)
  library(fst)
  library(future)
  library(here)
  library(nngeo)
  library(ggplot2)
  library(SHAPforxgboost)
  library(Just.universal)
})
